DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-06-13 2015CompleteDerivation/completeDerivation.tex
Adding justifications for relativistic Hamiltonian

%Status: conceptual work is done, need to write down

@@

\begin{justification}
	TODO
\end{justification}

@@

\begin{justification}
	TODO
\end{justification}

@@

\begin{justification}
	TODO
\end{justification}

@@

\begin{prop}\label{form_of_extended_hamiltonian}
	The form of the extended Hamiltonian is $\mathcal{H} = \lambda(t,E,q^i,p_i) \, (H(t,q^i,p_i) - E)$ where $H(t,q^i,p_i)$ is the standard Hamiltonian at each instant $t$, the conjugate time variable $E = H(t,q^i,p_i)$ represents the value of the Hamiltonian, and  $\lambda : T^*\mathcal{M} \rightarrow \mathbbm{R}$ where $\lambda(\xi^a) = d_s t$.
\end{prop}

\begin{justification}
	TODO
\end{justification}

@@

\begin{justification}
	TODO
\end{justification}

>>>>

% Review started

@@

\begin{justification}
	We claim $\mathcal{T}_{\Delta s}$ is a self-homeomorphism on $T^*\mathcal{M}$. The extended state space for particles of a homogeneous classical material is $T^*\mathcal{M}$ by \ref{classical_extended_phase_space}. $\mathcal{T}_{\Delta s}$ is a deterministic and reversible evolution map and by \ref{detrevmap} is a self-homeomorphism.

	We claim $\mathcal{T}_{\Delta s}$ is a symplectomorphism on $(T^*\mathcal{M}, \omega)$. The distribution on final states must be defined. The Jacobian for $\mathcal{T}_{\Delta s}$ exists and is non-zero. $\mathcal{T}_{\Delta s}$ is a diffeomorphism. A deterministic and reversible process conserves the number of states and possibilities. $\omega$ is the metric for the cardinality of possibilities. $\omega$ is invariant under a deterministic and reversible evolution map. $\mathcal{T}_{\Delta s}$ is a symplectomorphism by definition.\end{justification}

@@

\begin{justification}
We claim the vector field $S \in T(T^*\mathcal{M})$ for the infinitesimal displacement $S^a = d\xi^a/dt$ admits a potential $\mathcal{H}$ such that $S^{a} \omega_{ab} = \partial_{b}\mathcal{H}$. The extended state space $T^*\mathcal{M}$ of a classical homogeneous material is a symplectic manifold by \ref{classical_extended_phase_space}. The map for infinitesimal time evolution $\mathcal{T}_{dt}$ is an infinitesimal self-symplectomorphism by \ref{relativistic_canonical_transformation}. By \ref{symplectomorphism_generator} the infinitesimal displacement $S$ admits a potential $\mathcal{H}$ such that $S^{a} \omega_{ab} = \partial_{b}\mathcal{H}$

We claim the state variables evolve according to extended Hamilton's equations. $S^{a} \omega_{ab} = d_s\xi^a \omega_{ab} = \partial_{b}\mathcal{H}$. For $a = 0$ we have $d_s t \, (-1) = \partial_{E} \mathcal{H}$. For  $a=\{1,...,n\}$ we have $d_s q^i \, (+1) = \partial_{p^i} \mathcal{H}$. For $a=n+1$ we have $d_s E \, (+1) = \partial_{t} \mathcal{H}$. For $a=\{n+2,...,2n + 1\}$ we have $d_s p_i \, (-1) = \partial_{q^i} \mathcal{H}$.
\end{justification}

@@

\begin{justification}
	We claim $t(s)$ is strictly monotonic. The motion is deterministic and reversible. At each value of $t$ there must be only one possible state: if there is more then one state the motion is non-deterministic (one state is not enough to identify them), if there is no state the motion is non-reversible (no state cannot identify a state). $t(s)$ is invertible. $t(s)$ is strictly monotonic.

	We claim $d_{s}t$ partitions the space. Let $\mathcal{s}_1, \mathcal{s}_2 \in T^*\mathcal{M}$ two physical states connected by deterministic and reversible evolution. $\mathrm{sign}(d_{s}t(\mathcal{s}_1)) = \mathrm{sign}(d_{s}t(\mathcal{s}_2))$. Let $U \equiv \{\mathcal{s} \in T^*\mathcal{M} \; | \; d_{s}t(\mathcal{s}) > 0 \}$ and $V \equiv \{\mathcal{s} \in T^*\mathcal{M} \; | \; d_{s}t(\mathcal{s}) < 0 \}$. $U \cap V = \varnothing$. Let $\gamma : [s_0, s_1] \rightarrow T^*\mathcal{M}$ the trajectory given by deterministic and reversible evolution. Either $\gamma([s_0, s_1]) \subseteq U$ or $\gamma([s_0, s_1]) \subseteq V$.
\end{justification}

@@

\begin{prop}\label{form_of_extended_hamiltonian}
	The form of the extended Hamiltonian is $\mathcal{H} = \lambda(t,E,q^i,p_i) \, (H(t,q^i,p_i) - E)$ where $H(t,q^i,p_i)$ is the standard Hamiltonian at each instant $t$, the conjugate time variable $E = H(t,q^i,p_i)$ represents the value of the Hamiltonian, and  $\lambda : T^*\mathcal{M} \rightarrow \mathbbm{R}$ where $\lambda(\xi^a) = d_s t$. $\mathcal{H} = 0$ for all states at all time.
\end{prop}

\begin{justification}
	We claim the form of the extended Hamiltonian is $\mathcal{H} = \lambda(t,E,q^i,p_i) \, (H(t,q^i,p_i) - E)$. Let $\mathcal{H}$ the extended Hamiltonian and $H$ be Hamiltonian for a particular choice of time and state variables. We have $d_s q^i = \partial_{p_i} \mathcal{H} = d_s t \, d_t q^i = - \lambda \, \partial_{p_i} H$ where $\lambda : T^*\mathcal{M} \rightarrow \mathbbm{R} \; | \; \lambda \mapsto d_s t$. $d_s p_i = - \partial_{q^i} \mathcal{H} = d_s t \, d_t p_i = \lambda \, \partial_{q^i} H$. As $\lambda \neq 0$ for all physical states, we can set $\mathcal{H} = \lambda(t,E,q^i,p_i) \, (H(t,q^i,p_i) - E + \mathcal{h}(t,E,q^i,p_i))$ without loss of generality. We have $\partial_{q^i} \lambda (H - E + \mathcal{h}) + \lambda (\partial_{q^i} H + \partial_{q^i} \mathcal{h}) = \lambda \, \partial_{q^i} H$. This holds for all choices of $t$. In particular for $t=s$, $\lambda (\partial_{q^i} H + \partial_{q^i} \mathcal{h}) = \lambda \, \partial_{q^i} H$. $\partial_{q^i} \mathcal{h} = 0$. $\mathcal{h}$ is not a function of $q^i$. Repeat the same procedure for $p_i$. $\mathcal{h}$ is not a function of $p_i$. $\lambda = d_s t = - \partial_E \mathcal{H} = - \partial_{E} \lambda (H - E + \mathcal{h}) - \lambda (-1 + \partial_{E} \mathcal{h})$. In particular for $t=s$, $\lambda = - \lambda (-1 + \partial_{E} \mathcal{h})$. $\partial_{E} \mathcal{h} = 0$. $\mathcal{h}$ is not a function of $E$. $\mathcal{h}$ is only a function of $t$. We can redefine $H = H + \mathcal{h}$ as the result is still a function of $q^i, p_i , t$ with the same equations of motion.

	We claim $E = H(t,q^i,p_i)$ for physical states. $\lambda = d_s t = - \partial_E \mathcal{H} = - \partial_{E} \lambda (H - E + \mathcal{h}) - \lambda (-1)$ for any choice of $t$. $H - E = 0$.

	We claim $\mathcal{H} = 0$ for physical states. $\mathcal{H} = \lambda (H - E) = 0$.
\end{justification}

@@

\begin{justification}
	We claim $\mathcal{H} \rho_\mathcal{c}(s) = 0 \; \forall \mathcal{c} \in \mathcal{C} \wedge s \in \mathbbm{R}$. Let $\rho_\mathcal{c}(s) : T^*\mathcal{M} \rightarrow \mathbbm{R}$ be the distribution associated with a composite state $\mathcal{c}$ at a given value of $s$. The distribution is defined on physical states. By \ref{form_of_extended_hamiltonian} $supp(\rho_\mathcal{c}(s)) \subseteq T^*\mathcal{M} \,\backslash\, supp(\mathcal{H})$. $supp(\mathcal{H} \rho_\mathcal{c}(s)) = supp(\mathcal{H}) \cap supp(\rho_\mathcal{c}(s)) \subseteq \varnothing$.

	We claim $d_s \rho_\mathcal{c} (s) = \{ \rho_\mathcal{c}(s), \mathcal{H} \}$. Let $\rho_\mathcal{c} (s)$ be differentiable. $d_s \rho_\mathcal{c}(s) = \partial_a \rho_\mathcal{c}(s) d_s \xi^a = \partial_a \rho_\mathcal{c}(s) \omega^{ab} \partial_b \mathcal{H} = \{ \rho_\mathcal{c}(s), \mathcal{H} \}$.

	We claim $\mathcal{H} \rho_\mathcal{c} = 0 \; \forall \mathcal{c}$. Let $\rho_\mathcal{c} : T^*\mathcal{M} \rightarrow \mathbbm{R}$ be the distribution associated with a composite state $\mathcal{c}$ at all states at all times. The distribution is defined on physical states. By \ref{form_of_extended_hamiltonian} $supp(\rho_\mathcal{c}) \subseteq T^*\mathcal{M} \,\backslash\, supp(\mathcal{H})$. $supp(\mathcal{H} \rho_\mathcal{c}) = supp(\mathcal{H}) \cap supp(\rho_\mathcal{c}) \subseteq \varnothing$.

	We claim $d_s \rho_\mathcal{c} = \{ \rho_\mathcal{c}(s), \mathcal{H} \} = 0$. Let $\rho_\mathcal{c}$ be differentiable. $d_s \rho_\mathcal{c}= \partial_a \rho_\mathcal{c} d_s \xi^a = \partial_a \rho_\mathcal{c}(s) \omega^{ab} \partial_b \mathcal{H} = \{ \rho_\mathcal{c}, \mathcal{H} \}$. Let $\gamma : \mathbbm{R} \rightarrow T^*\mathcal{M}$ a particle trajectory. Then $\rho_\mathcal{c}(\lambda(s)) = \rho_\mathcal{c}(\lambda(s + \Delta s))$. $d_s \rho_\mathcal{c} = 0$.
